Tropical Andes plant species BIEN data

### 2023-07-18 code/L0/L0_TropicalAndes_plants_BIEN_occ.Rmd
update file path

# Write data to csv
```{r}
TropicalAndes_BIEN_occurrence_path <- file.path(output_path,"TropicalAndes_BIEN_occurrence.csv") 
write.csv(TropicalAndes_BIEN_occ, file = TropicalAndes_BIEN_occurrence_path)

>>>>

# Write data to csv
```{r}
TropicalAndes_BIEN_occurrence_path <- file.path(output_path,"TropicalAndes_BIEN_occ.csv") 
write.csv(TropicalAndes_BIEN_occ, file = TropicalAndes_BIEN_occurrence_path)
